---
title: Tipping Bucket Rain Gauge QAQC Report for  `r location_i`, `r examineYear `
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: yes 
    number_sections: true  
    center: true
    highlight: tango
    theme: spacelab
---

```{r Global options, include=FALSE}

library(hydroGOF)
library(plotly)
library(DT)
library(lubridate)
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


> Data used in this report are from "02_test4review" folder.

# Heatmap Plot of Hourly Rain Data  
  
Below shows a heatmap for hourly rain `r data_type_all[[1]]` data.  
```{r HeatmapCampbell, fig.height = 6, out.width = "100%"}
plot_p[[1]]
```
  
  
```{r HeatmapHoBo, fig.height = 6, out.width = "100%"}
if (length(plot_p) == 2){
print(paste0("Below shows a heatmap for hourly rain ", data_type_all[[2]]," data.  "))
  
    plot_p[[2]]
} else {
    print("This location only has one data.")
  }
```
  
    
# Daily rain data

This table shows the data for goodness-of-fit evaluation, location `r location_i`, year `r examineYear`.   
Time span for the data is `r min(data_day_join$date)` to `r max(data_day_join$date)`.
```{r data_day_join}
DT::datatable(data_day_join, caption = "Daily rain (mm)", 
              filter = 'top', 
              extensions = 'Buttons',
              options = list(dom ='Bfrtip', 
                             buttons=c('copy', 'csv', 'excel', 'print', 'pdf'),
                             autoWidth = TRUE, 
                             iDisplayLength = 10))

```

# Goodness-of-fit evaluation between Compbell and Hobo datasets

Goodness-of-fit evaluation starts on `r GOFstart`, ends on `r GOFend`. Please see the table below for all indicators.  
  
```{r gofDayPlot, fig.width=10, fig.height=6}
  ggplotly(plot_gof_day)  
```
   
   
```{r gofDayTable}

if (exists("GOFresultDay")){

DT::datatable(GOFresultDay, caption = "Goodness of fit result",
              extensions = 'Buttons',
              options = list(dom ='Bfrtip', 
                             buttons=c('copy', 'csv', 'excel', 'print', 'pdf'),
                             scrollX = TRUE))
  
} else {print("GOF result for this location does not exist.")}

```
  
<details>
<summary>GOF indicator explanation table (click to unfold) </summary>
  
| Indicator name |  Meaning |
|:---|:------------------|
|me   |Mean Error|
|mae	|Mean Absolute Error|
|rmse	|Root Mean Square Error|
|nrmse	|Normalized Root Mean Square Error|
|PBIAS	|Percent Bias|
|pbiasfdc|PBIAS in the slope of the midsegment of the Flow Duration Curve|
|RSR	|Ratio of RMSE to the Standard Deviation of the Observations, RSR = rms / sd(obs). ( 0 <= RSR <= +Inf )|
|rSD	|Ratio of Standard Deviations, rSD = sd(sim) / sd(obs)|
|NSE	|Nash-Sutcliffe Efficiency ( -Inf <= NSE <= 1 )|
|mNSE|Modified Nash-Sutcliffe Efficiency|
|rNSE	|Relative Nash-Sutcliffe Efficiency|
|d	|Index of Agreement ( 0 <= d <= 1 )|
|md	|Modified Index of Agreement|
|rd	|Relative Index of Agreement|
|cp	|Persistence Index ( 0 <= PI <= 1 )|
|r	|Pearson product-moment correlation coefficient ( -1 <= r <= 1 )|
|r.Spearman	|Spearman Correlation coefficient ( -1 <= r.Spearman <= 1 )|
|R2	|Coefficient of Determination ( 0 <= R2 <= 1 ). Gives the proportion of the variance of one variable that is predictable from the other variable|
|bR2	|R2 multiplied by the coefficient of the regression line between sim and obs ( 0 <= bR2 <= 1 )|
|KGE	| Kling-Gupta efficiency between sim and obs ( 0 <= KGE <= 1 )|
|VE	| Volumetric efficiency between sim and obs( -Inf <= VE <= 1)|
  
</details>
  
 
  
# Rain and Air Temperature   
  
This plot displays the hourly air temperature and rainfall data for both Campbell and Hobo datasets. The corresponding hourly data is also provided in the table below.
  
```{r tempRainPlot, fig.width=11, fig.height=7}

ggplotly(plot_temp_rain_hr, tooltip = c("TimestampH", "Tair_Avg_C", "text"), originalData = FALSE)

```
> This plot displays hourly rainfall data (in mm). Any missing data in the 'forReview' Excel table are indicated as -1 in this plot. However, in the data table below, missing values are still denoted as -99.


```{r tempRainTable}

DT::datatable(data_hour_all, 
              caption = "Hourly temperature and rain", 
              filter = 'top', 
              extensions = 'Buttons',
              options = list(dom ='Bfrtip', 
                             buttons=c('copy', 'csv', 'excel', 'print', 'pdf'),
                             autoWidth = TRUE, 
                             iDisplayLength = 10))

```
   
> Please run `App.R` in RStudio to see the cumulative rainfall plot.

  